When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-03-01 presentation/inbreeding.Rmd
Major updates with images

## Inbreeding

- Define relatedness

## Inbreeding depression

- What inbreeding depression is, exactly.

## Inbreeding depression

- What are the consequences of inbreeding depression.

@@

- Much different assumptions
- See if we can get a similar answer

@@

>>>>

## Biparental inbreeding theory

![](images/female.png)

![](images/male.png)

Monster images: [http://cliparts.co](http://cliparts.co)

## Pedigrees and coefficients affecting inbreeding

<center>
![](images/pedigree_1.png)
</center>

## Pedigrees and coefficients affecting inbreeding

<center>
![](images/pedigree_2.png)
</center>

## Pedigrees and coefficients affecting inbreeding

<center>
![](images/pedigree_3.png)
</center>

## Pedigrees and coefficients affecting inbreeding

<center>
![](images/pedigree_4.png)
</center>

## Pedigrees and coefficients affecting inbreeding

<center>
![](images/pedigree_5.png)
</center>

## Pedigrees and coefficients affecting inbreeding

<center>
![](images/pedigree_6.png)
</center>

## Pedigrees and coefficients affecting inbreeding

<center>
![](images/pedigree_7.png)
</center>

## Pedigrees and coefficients affecting inbreeding

<center>
![](images/pedigree_8.png)
</center>

## Inbreeding depression ($\delta$) slopes ($\beta$)

```{r, echo = FALSE, fig.width = 4}
fcoeff   <- seq(from = 0, to = 1, length = 1000);
survB0   <- rep(1, 1000);
survB0p2 <- exp(-1*0.2*fcoeff);
survB1   <- exp(-1*1*fcoeff);
survB2   <- exp(-1*2*fcoeff);
survB5   <- exp(-1*5*fcoeff);
par(mar = c(5, 5, 1, 0.5));
plot(x = 0, y = 0, type = "n", xlab = "Inbreeding coefficient (f)",
     ylab = expression(paste("Pr. offspring survival (1 - ",delta,")")),
     xlim = c(0, 1), ylim = c(0, 1), cex.lab = 1.5, cex.axis = 1.5);
points(x = fcoeff, y = survB0, type = "l", lwd = 3);
points(x = fcoeff, y = survB0p2, type = "l", lwd = 3);
points(x = fcoeff, y = survB1, type = "l", lwd = 3);
points(x = fcoeff, y = survB2, type = "l", lwd = 3);
points(x = fcoeff, y = survB5, type = "l", lwd = 3);
text(x = 0.8, y = 0.94, labels = expression(beta == 0), cex = 1.5);
text(x = 0.8, y = 0.79, labels = expression(beta == 0.2), cex = 1.5, srt = -8);
text(x = 0.7, y = 0.43, labels = expression(beta == 1), cex = 1.5, srt = -24);
text(x = 0.5, y = 0.30, labels = expression(beta == 2), cex = 1.5, srt = -32);
text(x = 0.3, y = 0.14, labels = expression(beta == 5), cex = 1.5, srt = -40);
```

<br>

- Inbreeding depression ($\delta$) generally increases with inbreeding coefficient ($f$)

- Offspring fitness ($1 - \delta$) consequently decreases with $f$

- Slope of decrease in offspring fitness defines $\beta$

@@

- Much different assumptions
- Stochasticity
- See if we can get a similar answer

## Individuals

<center>
![](images/individuals.png)
</center>

## Individuals

<center>
![](images/individuals_1.png)
</center>

## Individuals

<center>
![](images/individuals_2.png)
</center>

## Individual interactions

<center>
![](images/ibm_general_1.png)
</center>

## Individual interactions

<center>
![](images/ibm_general_2.png)
</center>

## Individual interactions

<center>
![](images/ibm_general_3.png)
</center>

## Individual-based modelling questions

- **When should we predict selection for a mutant allele causing pre-copulatory inbreeding avoidance or inbreeding preference? [1]**

- **Why should we predict females will mate multiply to adjust the degree to which they inbreed? [2]**

- **How should we predict females to avoid inbreeding (pre- versus post-copulatory avoidance)? [3]**

<br><br><br><br>

<hr>
<span style="font-size: 18px;">
1. Duthie, AB & JM Reid (2016) *Am. Nat.* [**188**:651-667](https://bradduthie.github.io/Duthie_Reid2016.pdf). <br>
2. Duthie, AB et al. (2016) *Evolution* [**70**:1927-1943](https://bradduthie.github.io/DuthieEtAl2016b.pdf). <br>
3. Duthie, AB et al. (2018) *J. Evol. Biol.* [**31**:31-45](https://bradduthie.github.io/DuthieEtAl2017.pdf). <br>
</span>

@@

## Simulated kinships vs. Mandarte song sparrows

<br>

```{r, echo = FALSE, fig.width = 4}
renderPlot({
  par(bg = 'transparent');
  malle <- iter$all;
  mneut <- iter$nue
  mkval <- iter$mkv
  gens  <- 1:length(iter$all);
  par(mar = c(7, 5, 5, 5));
  hist(iter$kva, xlim = c(0, 1), ylim = c(0, 20), freq = FALSE, col = "black",
        yaxt = "n", ylab = "", main = "", xlab = "", 
        breaks = seq(from = 0, to = 1, by = 0.05), cex.axis = 1.5);
  title(xlab = "Kinship (k)", line = 4, cex.axis = 1.5, cex.lab = 1.5);
  box(lwd = 3);
})
```

![](images/sparrow_pedigree.png)
